Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-06 vesicle_code/docs/adhesion/adhesion.tex
changes from yny

The dynamics of weakly adhesive vesicles under various flowing
conditions is investigated numerically using a high-order
adaptive-in-time boundary integral equation formulation. In a quiescent
flow, two vesicles move slowly towards each other under the adhesive
potential, pushing out fluid in the gap to form a doublet at
equilibrium. A lubrication analysis on such draining of the thin film
gives the dependencies of draining time on adhesion strength and
separation distance that are in good agreement with numerical results.
%
In a microfluid trap where the stagnation of an extensional flow is
placed in the middle of a vesicle doublet through an active control
loop, novel dynamics of a vesicle doublet are observed. Numerical
simulations show that there exists a critical extensional flow rate
above which the weak adhesive interaction is overcome by the
hydrodynamic diverging stream, thus providing a simple method to measure
the adhesion strength between two vesicle membranes. 
%
In a planar shear flow, numerical simulations reveal that a vesicle
doublet may form as they approach each other provided that the adhesion
strength is sufficient large at a given vesicle reduced area. Once a
doublet is formed, the effective shear viscosity of a dilute suspension
of vesicle doublets is found to be a function of both reduced area and
the adhesion strength.  Results from these numerical studies and
analysis shed light on the hydrodynamic effects of adhesive interactions
between vesicles in a viscous fluid.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

@@

\section{Introduction}
Vesicles (closed fluid-filled phospholipid bilayer membranes) have been
widely utilized as biological cell mimics in biophysics and material
engineering \cite{sackmann1996}.  The ever expanding applications have
encouraged detailed experimental, theoretical, and numerical
investigations of vesicle hydrodynamics in applied flow, electric
fields, and magnetic fields.  Theoretical investigations often take the
form of small-deformation analysis or spheroidal dynamics of a
nearly-spherical vesicle (or nearly-circular in two dimensions)
subjected to an applied flow or under an external
forcing~\cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
Vlahovska2007_PRE, Finken2008_EPL, ZhangZahnTanLin2013_PoF,
Nganguia2013_PRE}.  On the other hand, various numerical methods have
been developed for simulating the transient hydrodynamics of vesicle
suspensions~\cite{BagchiJohoson2005_JBE, Biben2005_EJP,
Veerapaneni2009_JCP, SeolHuKimLai2016_JCP}.

Hydrodynamics of a single vesicle in Stokes flow has been extensively
investigated. In a planar shear flow, the vesicle hydrodynamics is
characterized by the reduced volume (reduced area in two dimensions),
viscosity contrast between interior and exterior fluids, and shear rate
of the imposed far-field fluid flow. In addition, a vesicle with a rigid
particle inside is also investigated as a biological mimic of a
eukaryotic cell with a nucleus that occupies nearly half of the
intracellular volume~\cite{Veerapaneni2011_PRL}. Small-deformation
analysis shows that a vesicle tank-treads in a planar shear flow for low
viscosity contrast and shear rate. At high viscosity contrast the
tank-treading dynamics transitions to tumbling 
dynamics~\cite{Misbah2006_PRL, Vlahovska2007_PRE}, and this leads to a
transition in effective shear viscosity in the vesicle
suspension~\cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
by direct numerical simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
experiments~\cite{KantslerSegreSteinberg2008_EPL,
ZabuskySegreDeschamps2011_PoF}.  Between tank-treading and tumbling
vesicle dynamics, a breathing (tremble) mode is also
observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,
ZhaoShaqfeh2011_JFM, SpannZhaoShaqfeh2014_PoF} to affect the effective
shear viscosity in a different way.  In an extensional flow (planar or
uniaxial), vesicle shape dynamics depends sensitively on the vesicle
reduced volume and the elastic capillary
number~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape
and oscillatory undulation of the vesicle membrane are two examples of
the complex vesicle hydrodynamics in an extensional flow.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
The adhesion model of Sukumaran and Seifert~\cite{suk-sei2001} considers
adhesion between a single three-dimensional vesicle and a solid wall at
$z=0$.  They use the adhesion potential of the function form
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = H \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $z$ is the distance between the solid wall and the vesicle,
$\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
scale and $(m,n) = (4,2)$.  We generalize this model to an unbounded
suspension of vesicles.  We assume that the adhesion force applies
between all pairs of points on different vesicles, so we are interested
in Hamaker constants that are appropriate for lipid-lipid interactions.
In Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}
The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.

@@

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
  \caption{\label{fig:Dec18_vesicle_shape} Two vesicles of length $\pi$
  with $\kappa=1$, $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}:
  Equilibrium shapes of two vesicles under adhesive interactions with
  adhesion strength $\mathcal{H}=5$ and separation distance
  $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
  are labeled.  The color coding is the tension along the vesicle. {\em
  Right}: Membrane shapes in the contact region.} \todo[inline]{This
  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
  = 5$?}
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a L-J potential ($(m,n) =
(12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
decreases further, we observe undulation of the elongated equilibrium
vesicle shape on the non-contact side while the contact region remains
flat.  The color coding along each curve is the tension of the vesicle
membrane.  We observe that the membrane tension in the contact region is
very negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
  \caption{\label{fig:Dec18_vesicle_equilibrium1} Two vesicles of length
  $\pi$ with $\kappa=1$, $\mathcal{H}=5$ and $\delta=0.2$.  {\em Left}:
  Total bending energy (solid curve) and adhesion energy (dash-dotted
  curve) plotted against the reduced area $\Delta A$. {\em Right}: Sum
  of two energies plotted against reduced area $\Delta A$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{sec:conclusions}}
In this work we use boundary integral formulation with adaptive
time-stepping to simulate hydrodynamics of two vesicles with adhesive
interactions.  In a quiescent flow, two vesicles that are initially
sufficiently far apart move towards each other under a long-range
attraction.  We use a lubrication theory to estimate the time required
to reach the separation distance, and the theoretical scaling is in good
agreement with numerical results.  Once two membranes are within
separation distance $\delta$, the adhesive force turns repulsive and the
membranes flatten to form a contact region.  Our simulations show that
the membranes in the contact region are actually curved with end points
at the shortest distance.  Once a vesicle doublet forms, we examine the
dependence of membrane bending and adhesion energies on the reduced
area, the Hamaker constant, and the separation distance.

Next we conduct a numerical experiment where a vesicle doublet is placed
at the center of a fluid trap, which can be actively controlled in
microfluidic channel so that fluid trap center is effectively the
stagnation point of an extensional flow characterized by a extensional
flow rate.  At low flow rate, we find the doublet to rotate nearly ninety
degrees to align with the flow such that the long axis of the doublet is
along the divergent axis and the convergent stream is pushing the two
vesicles together. As the flow rate increases, the vesicle doublet
rotates less, and when the flow rate reaches above the critical value,
the diverging flow breaks the doublet structure by pulling the vesicles
apart.  These results indicate that it is possible to use the fluid trap
to separate a vesicle doublet under adhesion, and thus provide a means
to probe the adhesion strength between membranes.  For a pair of $\mu
m$-sized vesicles with a bending rigidity of $\sim 10^{-19}$ $J$, an
extensional flow rate of $0.5$ $s^{-1}$ is expected to separate a
vesicle doublet with reduced area of $\Delta A = 0.8$ and a Hamaker
constant $\mathcal{H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$.
These conditions are quite realizable in microfluidic experiments, and
we hope that our simulations will inspire microfluidic experiments.

We also examine how adhesive interaction may lead to formation of a
vesicle doublet dynamically in flowing conditions.  We simulate two
vesicles approaching each other in a planar shear flow, and examine how
their adhesive interactions lead to doublet formation.  Once a doublet
forms, the two vesicle membranes rotate around each other as they deform
dynamically. The usual tank-treading motion of a vesicle under shear
flow is not observed in each of the two vesicles. We also compute the
effective shear viscosity of a dilute suspension of vesicle doublets,
and found that membrane adhesion contribution increases with decreasing
reduced area because deflated vesicles (low reduced area) deform more
easily and more membranes in the contact region.
\todo[inline]{I don't understand this last sentence}

@@

Future work includes three dimensional simulations, viscosity contrast,
dense suspensions, and confined suspensions.  In
Figure~\ref{fig:relaxationManyVes} illustrate snapshots of five vesicles
suspended inside of a larger vesicle.  There is no imposed flow, so the
dynamics are governed entirely by the adhesion, bending, and tension
forces.  In the absence of confinement, we would expect the vesicles to
align themselves as a rouleaux with the membranes forming a parachute,
male-female, or S-shape
configurations~\cite{FlormannAouane2017_SciReports}.  However, because
of the bounding vesicle and the dense packing, the interior vesicles
align themselves differently.  In addition, several parts of the
bounding membrane closely follow the interior membranes in order to
minimize the adhesion energy.  In
Figure~\ref{fig:relaxationManyVesAdhesionTension} we plot the tension
(left) and adhesion (right) of the final equilibrium configuration.

>>>>

The dynamics of adhesive vesicles under various flowing
conditions is investigated numerically using a high-order
adaptive-in-time boundary integral equation formulation. In a quiescent
flow, two nearby vesicles move slowly towards each other under the adhesive
potential, pushing out fluid in the gap to form a doublet at
equilibrium. A lubrication analysis on such draining of the thin film
gives the dependencies of draining time on adhesion strength and
separation distance that are in good agreement with numerical results.
%
In a microfluid trap where the stagnation of an extensional flow is
placed in the middle of a vesicle doublet through an active control
loop, novel dynamics of a vesicle doublet are observed. Numerical
simulations show that there exists a critical extensional flow rate
above which the weak adhesive interaction is overcome by the
hydrodynamic diverging stream, thus providing a simple method to measure
the adhesion strength between two vesicle membranes. 
%
In a planar shear flow, numerical simulations reveal that a vesicle
doublet may form as they approach each other provided that the adhesion
strength is sufficient large at a given vesicle reduced area. Once a
doublet is formed, the effective shear viscosity of a dilute suspension
of vesicle doublets is found to be a function of both reduced area and
the adhesion strength.  Results from these numerical studies and
analysis shed light on the hydrodynamic effects of adhesive interactions
between vesicles in a viscous fluid.
%\begin{description}
%\item[Usage]
%Secondary publications and information retrieval purposes.
%\item[PACS numbers]
%May be entered using the \verb+\pacs{#1}+ command.
%\item[Structure]
%You may use the \texttt{description} environment to structure your abstract;
%use the optional argument of the \verb+\item+ command to give the category of each item. 
%\end{description}
\end{abstract}

@@

\section{Introduction}
Vesicles (closed fluid-filled phospholipid bilayer membranes) have been
widely utilized as biological cell mimics in biophysics and material
engineering \cite{sackmann1996,Barthes-Biesel2016_ARFM}.  The ever expanding applications have
encouraged detailed experimental, theoretical, and numerical
investigations of vesicle hydrodynamics in applied flow, electric
fields, and magnetic fields.  Theoretical investigations often take the
form of small-deformation analysis or spheroidal dynamics of a
nearly-spherical vesicle (or nearly-circular in two dimensions)
subjected to an applied flow or under an external
forcing~\cite{Barthes-BieselRallison1981_JFM, Misbah2006_PRL,
Vlahovska2007_PRE, Finken2008_EPL, ZhangZahnTanLin2013_PoF,
Nganguia2013_PRE}.  On the other hand, various numerical methods have
been developed for simulating the transient hydrodynamics of vesicle
suspensions~\cite{BagchiJohoson2005_JBE, Biben2005_EJP,
Veerapaneni2009_JCP, SeolHuKimLai2016_JCP}.

Hydrodynamics of a single vesicle in Stokes flow has been extensively
investigated. In a planar shear flow, the vesicle hydrodynamics is
characterized by the reduced volume (reduced area in two dimensions),
viscosity contrast between interior and exterior fluids, and shear rate
of the imposed far-field fluid flow. In addition, a vesicle with a rigid
particle inside is also investigated as a biological mimic of a
eukaryotic cell with a nucleus that occupies nearly half of the
intracellular volume~\cite{Veerapaneni2011_PRL}. Small-deformation
analysis shows that a vesicle tank-treads in a planar shear flow for low
viscosity contrast and shear rate. At high viscosity contrast the
tank-treading dynamics transitions to tumbling 
dynamics~\cite{Misbah2006_PRL, Vlahovska2007_PRE}, and this leads to a
transition in effective shear viscosity in the vesicle
suspension~\cite{Misbah2006_PRL,Vitkova2008_BJ} that is also validated
by direct numerical simulations~\cite{GhigliottiBibenMisbah2010_JFM} and
experiments~\cite{DeschampsKantsler2009_PNAS,KantslerSegreSteinberg2008_EPL,
ZabuskySegreDeschamps2011_PoF}.  Between tank-treading and tumbling
vesicle dynamics, a breathing (tremble) mode is also
observed~\cite{Misbah2006_PRL,KantslerSegreSteinberg2008_PRL,
ZhaoShaqfeh2011_JFM, SpannZhaoShaqfeh2014_PoF} to affect the effective
shear viscosity in a different way.  In an extensional flow (planar or
uniaxial), vesicle shape dynamics depends sensitively on the vesicle
reduced volume and the elastic capillary
number~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}: Asymmetric shape
and oscillatory undulation of the vesicle membrane are two examples of
the complex vesicle hydrodynamics in an extensional flow.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adhesion Model}
Sukumaran and Seifert~\cite{suk-sei2001} considers
adhesion between a single three-dimensional vesicle and a solid wall at
$z=0$.  They use the adhesion potential of the function form
\begin{align}
\label{eq:adhesion_potential}
  \phi(z) = H \left[ 
    \left(\frac{\delta}{z}\right)^m - \frac{m}{n} \left(\frac{\delta}{z}\right)^n \right],
\end{align}
where $z$ is the distance between the solid wall and the vesicle,
$\mathcal{H}$ is the Hamaker constant, $\delta$ is the adhesion length
scale and $(m,n) = (4,2)$.  We generalize this model to an unbounded
suspension of vesicles.  We assume that the adhesion force applies
between all pairs of points on different vesicles, so we are interested
in Hamaker constants that are appropriate for lipid-lipid interactions.
In Appendix~\ref{sec:appendixA}, the adhesive force at a point $\xx$ on
vesicle $j$ is shown to be
\begin{align}
  \AA\xx:=-\mathcal{H} m \delta^{n}\sum_{\substack{k=1 \\ k \neq j}}^M 
  \int_{\gamma_k} \frac{\xx - \yy}{\|\xx - \yy\|^{m+2}} 
  \left(\delta^{m-n} - \|\xx - \yy\|^{m-n} \right) ds_\yy.
  \label{eqn:adhesionForce}
\end{align}
The adhesion model is illustrated in Figure~\ref{fig:adhesionModel}.

@@

In this work we focus on weakly adhesive vesicles whose equilibrium
shapes in a quiescent flow are shown in the left plot of
Figure~\ref{fig:Dec18_vesicle_shape} for three reduced areas: $\Delta
A=0.95$, $0.75$, and $0.6$ with $\mathcal{H}=5$ and $\delta = 0.2$. 
\begin{figure}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_00.jpeg}
  \includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_vesicle_shape_vs_rA_01.jpeg}
  \caption{\label{fig:Dec18_vesicle_shape} Two vesicles of the same length, reduced area
  and bending rigidity ($\kappa=1$)
  with $\mathcal{H}=5$, and $\delta=0.2$.  {\em Left}:
  Equilibrium shapes of two vesicles under adhesive interactions with
  adhesion strength $\mathcal{H}=5$ and separation distance
  $\delta=0.2$.  Vesicle reduced area $\Delta A=0.95$, $0.75$, and $0.6$
  are labeled.  The color coding is the tension along the vesicle. {\em
  Right}: Membrane shapes in the contact region.} \todo[inline]{This
  caption contradicts itself.  Is it $\mathcal{H} = 0.5$ or $\mathcal{H}
  = 5$?}
\end{figure}
The equilibrium vesicle shape for $\Delta A=0.95$ is the circular cap
with a flat contact region.  This is similar to the observed shapes of
two vesicles under strong adhesive interaction
in~\cite{RamachandranAndersonLealIsraelachvili2010_Langmuir}.  When
vesicles are more deflated with a reduced area $\Delta A = 0.75$, the
equilibrium vesicle shape is elongated with a bigger contact region.
This is consistent with the equilibrium shapes of a vesicle doublet
under a L-J potential ($(m,n) =
(12,6)$)~\cite{FlormannAouane2017_SciReports}.  As the reduced area
decreases further, we observe undulation of the elongated equilibrium
vesicle shape on the non-contact side while the contact region remains
flat.  The color coding along each curve is the tension of the vesicle
membrane.  We observe that the membrane tension in the contact region is
very negative, indicating a dominant compression of membrane when the
adhesion force is strong to keep the vesicles bound together.

@@

\begin{figure}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_Ebleft_Eadhright_vs_rA_adR0p2_adS502.jpeg}
\includegraphics[keepaspectratio=true,scale=0.175]{figs/Dec18_EbEadh_vs_rA_adR0p2_adS502.jpeg}
  \caption{\label{fig:Dec18_vesicle_equilibrium1} Two vesicles of the same length, reduced area
  and bending rigidity ($\kappa=1$)  with $\mathcal{H}=5$ and $\delta=0.2$.  {\em Left}:
  Total bending energy (solid curve) and adhesion energy (dash-dotted
  curve) plotted against the reduced area $\Delta A$. {\em Right}: Sum
  of two energies plotted against reduced area $\Delta A$.}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions\label{sec:conclusions}}
In this work we use boundary integral formulation with adaptive
time-stepping to simulate hydrodynamics of two vesicles with adhesive
interactions.  In a quiescent flow, two vesicles that are initially
sufficiently far apart move towards each other under a long-range
attraction.  We use a lubrication theory to estimate the time required
to reach the separation distance $\delta$, and the theoretical scaling is in good
agreement with numerical results.  Once two membranes are within
separation distance $\delta$, the adhesive force turns repulsive and the
membranes flatten to form a contact region.  Our simulations show that
the membranes in the contact region are actually curved with end points
at the shortest distance.  Once a vesicle doublet forms, we examine the
dependence of membrane bending and adhesion energies on the reduced
area, the Hamaker constant, and the separation distance.

Next we conduct a numerical experiment where a vesicle doublet is placed
at the center of a fluid trap, which can be actively controlled in
microfluidic channel so that fluid trap center is effectively the
stagnation point of an extensional flow characterized by a extensional
flow rate.  At low flow rate, we find the doublet to rotate nearly ninety
degrees to align with the flow such that the long axis of the doublet is
along the divergent axis and the convergent stream is pushing the two
vesicles together. As the flow rate increases, the vesicle doublet
rotates less, and when the flow rate reaches above the critical value,
the diverging flow breaks the doublet structure by pulling the vesicles
apart.  These results indicate that it is possib le to use the fluid trap
to separate a vesicle doublet under adhesion, and thus provide a means
to probe the adhesion strength between membranes.  For a pair of $\mu
m$-sized vesicles with a bending rigidity of $\sim 10^{-19}$ $J$, an
extensional flow rate of $0.5$ $s^{-1}$ is expected to separate a
vesicle doublet with reduced area of $\Delta A = 0.8$ and a Hamaker
constant $\mathcal{H}=0.7$, which corresponds to $\sim 1$ $\mu J/m^2$.
These conditions are quite realizable in microfluidic experiments, and
we hope that our simulations will inspire microfluidic experiments.

We also examine how adhesive interaction may lead to formation of a
vesicle doublet dynamically in flowing conditions.  We simulate two
vesicles approaching each other in a planar shear flow, and examine how
their adhesive interactions lead to doublet formation.  Once a doublet
forms, the two vesicle membranes rotate around each other as they deform
dynamically. The usual tank-treading motion of a vesicle under shear
flow is not observed in each of the two vesicles. We compute the
effective shear viscosity of a dilute suspension of vesicle doublets,
and found it to be more than twice the effective shear viscosity of a dilute suspension of single vesicles.
Furthermore, we find that the membrane adhesion contribution to the shear viscosity increases with decreasing
reduced area while the bending/tension contribution increases with the reduced area.
%
%because deflated vesicles (low reduced area) deform more
%easily and more membranes in the contact region.
\todo[inline]{I don't understand this last sentence --> modified now by yny}

@@

Future work includes three dimensional simulations, viscosity contrast,
dense suspensions, and confined suspensions. 
Figure~\ref{fig:relaxationManyVes} illustrate snapshots of five vesicles
suspended inside of a larger vesicle.  There is no imposed flow, so the
dynamics are governed entirely by the adhesion, bending, and tension
forces.  In the absence of confinement, we would expect the vesicles to
align themselves as a rouleaux with the membranes forming a parachute,
male-female, or S-shape
configurations~\cite{FlormannAouane2017_SciReports}.  However, because
of the bounding vesicle and the dense packing, the interior vesicles
align themselves differently.  In addition, several parts of the
bounding membrane closely follow the interior membranes in order to
minimize the adhesion energy.  In
Figure~\ref{fig:relaxationManyVesAdhesionTension} we plot the tension
(left) and adhesion (right) of the final equilibrium configuration.
